---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# islsdown

<!-- badges: start -->
<!-- badges: end -->

The goal of islsdown is to provide a boiler plate 

## Installation

### Package Installation

`islsdown` is currently under development on GitHub. Please install and test the package as follows:

```{r installation, eval = FALSE}
if(!require(remotes)) {
install.packages("remotes")
}

remotes::install_github('jooyoungseo/islsdown')
```

### TeX Installation

While not required for installation (as other LaTeX installations will likely also suffice), we recommend the use of the [{tinytex}](https://yihui.org/tinytex/) R package and associated LaTeX installation.

## Example

This is a basic example which shows you how to use `islsdown` package. While other formats are usable, `pdf` output is fully supported at this moment.

### Loading the package

```{r, eval = FALSE}
library(islsdown)
```

### For RStudio users

For RStudio users, as long as `islsdown` is installed, we recommend to create a new project which contains the file used for the contents of the manuscript (in `index.Rmd`, described more below) and other files used to render the file.

1. From within RStudio, select 
"File" -> 
"New Project" ->
"New Directory" and then select the *ISLS Annual Meeting* 
(`islsdown`) template.

2. Next, give your new directory a name, such as `my-isls-paper`.

3. Then, edit the `index.Rmd` document, which should automatically be open, but 
which can always be opened by selecting the file from its location in the
"Files" pane of RStudio. More instructions on editing the `index.Rmd` file are
provided in the "Using the template (index.Rmd)" section.

### For non-RStudio users

For non-RStudio users (or those looking to use the command line), 
you may create a project template in the current path with the following 
function:

```{r, eval = FALSE}
islsdown::islsdown_skeleton("my-isls-paper")
```

Then, edit the `index.Rmd` file. More instructions on editing the `index.Rmd` 
file are provided in the "Using the template (index.Rmd)" section.

## Rendering a PDF (or gitbook or Word) document from the template

Render the template to a document by clicking the 
"Knit" button at the top of the `index.Rmd` document. 

The result should be a PDF
document which appears like the document below.

To render a document to *a different output type* (other than a PDF), 
click the down arrow to the right of the "Knit" button, and select either the 
gitbook or Word document format.

# To-Do List

- [ ] Fully test `islsdown::isls_pdf()` format.
- [ ] Customize `islsdown::isls_word()` format.
- [ ] Update `README`.
- [ ] Write a simple vignette.
- [ ] Submit the package to CRAN.
- [ ] Write tutorial proposal for ISLS 2021.
